
\subsection*{\textbf{Question 1- Summary}}
\begin{quote}

\textbf{Summary}
\begin{quote}
The current sub-section contains the summary of the code used for assignment 1. This includes the file  containing all sub-questions and all used shared modules. 
\end{quote}


\textbf{Code - Assignment}

\begin{quote}
The code of the file that executes the sub-questions. The code presented below only consists of the part that has not jet been shown in the subquestions.  This part consists of the initialization of the random number generator (1.a) and the used imports. 
\label{CODE:MAIN1}
\lstinputlisting[firstline=0,lastline=18]{./Code/assigment_1.py}
\end{quote}

\textbf{Code - Random Number Generator} \\
\begin{quote}
The code for the random number generator.
\label{CODE:RNG}
\lstinputlisting{./Code/mathlib/random.py}
\end{quote}

\textbf{Code - Statistical functions} \\

\begin{quote}
The code that containing all statistical functions that where needed for the sub-questions. The imported sorting module used by this piece of code can be found on page 26. 
\label{CODE:Statistics}

\lstinputlisting{./Code/mathlib/statistics.py}
\end{quote}

\textbf{Code - Sorting} \\

\begin{quote}
The sorting algorithm used to sort the input of the KS-test and Kuiper-test.
\lstinputlisting{./Code/mathlib/sorting.py}
\label{CODE:Sorting}
\end{quote}
\end{quote}

\newpage

%\textbf{Code - output } 
%\begin{quote}
% The code that produces the output.
%\lstinputlisting{./code/assigment1_a.py}
%\end{quote}

%\textbf{Code - helper } 
%\begin{quote}
%The code for the Poisson distribution and the factorial function.  
%\lstinputlisting[firstline=2,lastline=46]{./code/mathlib/utils.py}
%\end{quote}


%\textbf{Output}
%\begin{quote}
%The output produced by \textsf{/code/assigment1\_ a.py} 
%\lstinputlisting{./output/assigment1_a_out.txt}
%\end{quote}
\newpage











