\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\input{./Tex/included_packages}

\renewenvironment{abstract}
 { \vspace*{0.3cm} \textbf{\abstractname} \vspace{0.1cm} \\ \ignorespaces}
 {\par\medskip \vspace{0.1cm}}

\setlength{\parindent}{0em}

\setlength{\textheight}{25.7cm}
\setlength{\textwidth}{18cm}
\setlength{\unitlength}{1mm}
\setlength{\topskip}{2truecm}

\topmargin 260mm \advance \topmargin -\textheight
\divide \topmargin by 2 \advance \topmargin -1in
\headheight 0pt \headsep 0pt \leftmargin 210mm \advance
\leftmargin -\textwidth
\divide \leftmargin by 2 \advance \leftmargin -1in
\oddsidemargin \leftmargin \evensidemargin \leftmargin
\parindent=0pt
\frenchspacing


%opening
\title{\vspace{-1cm}\textbf{Numerical Recipes for Astrophysics \\ Solutions hand-in assignment-2}}
\author{Luther Algra - s1633376}

\begin{document}

\maketitle
% two segments of code. The first segment of code contains the full code of the program that executes the sub-questions. The second segment contains the shared modules (if any) used by the sub-question.
\hrule
\begin{abstract}
The current document contains the solutions for the second hand-in assignment of Numerical Recipes. The main questions, 1, 2, 3 ..., 7, are in this document all given their own section. Each section contains a subsection for its related sub-questions (1.a, 1.b, 1.c, ..., 1.e) and ends with a final subsection that contains two segments of code. The first segment contains the code for the full main question. The second segment contains the code of shared modules used by the sub-questions. A sub-question itself always starts with a short summary of the question that needs to be answered. The summary is followed by an explanation of how the problem is solved and the code that provides the solution. If necessary some of the results are discussed here. The output of the code is always presented after the code and plots are discussed in their caption.


\end{abstract}
\hrule
\vspace{0.5cm}


\input{./Tex/assigment1.a}
\input{./Tex/assigment1.b}
\input{./Tex/assigment1.c}
\input{./Tex/assigment1.d}
\input{./Tex/assigment1.e}
\input{./Tex/assigment1.sum}
\input{./Tex/assigment2}
\input{./Tex/assigment3}
\input{./Tex/assigment4.a}
\input{./Tex/assigment4.b}
\input{./Tex/assigment4.c}
\input{./Tex/assigment4.d}
\input{./Tex/assigment4.sum}



\input{./Tex/assigment5.a}
\input{./Tex/assigment5.b}
\input{./Tex/assigment5.c}
\input{./Tex/assigment5.d}
\input{./Tex/assigment5.e}
\input{./Tex/assigment5.sum}




%\input{./Tex/assigment4.a}

\input{./Tex/assigment7}
%\input{./Tex/assigment3}





  







\end{document}
